Temporal stability in human interaction networks (Supporting Information document)

### 2015-11-02 supportingInformation.tex
arrumado nome do Paulo no SI

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)}% Force line breaks with \\

@@

%
%%\author{Luciano da Fontoura Costa}
%%  \homepage{http://cyvision.ifsc.usp.br/~luciano/}
%%  \email{ldfcosta@gmail.com}
%  \altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
%
\author{Leonardo Paulo Maia}
  \homepage{http://www.ifsc.usp.br/~lpmaia/}
  \email{lpmaia@ifsc.usp.br }
 \altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\

>>>>

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks (Supporting Information document)}% Force line breaks with \\

@@

%
%%\author{Luciano da Fontoura Costa}
%%  \homepage{http://cyvision.ifsc.usp.br/~luciano/}
%%  \email{ldfcosta@gmail.com}
%  \altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
%
\author{Leonardo P. Maia}
  \homepage{http://www.ifsc.usp.br/~lpmaia/}
  \email{lpmaia@ifsc.usp.br }
 \altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
